% \documentclass{resume} % Use the custom resume.cls style

\documentclass[11pt]{resume}

\usepackage{mathptmx} % Standard Times New Roman font
\usepackage{fontawesome5}
\usepackage[left=0.4 in,top=0.35in,right=0.4 in,bottom=0.35in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.1967\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\usepackage{enumitem}
\newcommand{\ptitle}[1]{{\fontsize{10.5}{12}\selectfont \textit{#1}}}
\newcommand{\ptitleb}[1]{{\fontsize{9}{10.5}\selectfont \textbf{#1}}}
\def\sectionskip{\smallskip}
\def\sectionlineskip{\smallskip}
\def\nameskip{\smallskip}
\def\addressskip{\vspace{0.05em}}

\setlist[itemize]{noitemsep, topsep=1pt}

\name{Anh Mai Vu}

% Note: the rSection class prints address calls in the order (3rd, 1st, 2nd),
% so the calls below are ordered to print as: contact line, LinkedIn, Google Scholar.
\address{\faLinkedin\ \href{https://www.linkedin.com/in/vu-mai-anh/}{LinkedIn: linkedin.com/in/vu-mai-anh}}
\address{\faGraduationCap\ \href{https://scholar.google.com/citations?user=vB0p8bYAAAAJ}{Google Scholar: scholar.google.com/citations?user=vB0p8bYAAAAJ}}
\address{Houston, TX | +1 (281) 780-0045 | mvu9@cougarnet.uh.edu}

\begin{document}

\begin{rSection}{Summary}

PhD student in Computer Engineering at the University of Houston seeking a Summer 2026 AI/ML Research Internship. Research focuses on trustworthy AI, explainable AI, computer vision, multimodal learning, medical image analysis, visual grounding, and human-centered AI. Experienced in Python, PyTorch, segmentation, weakly supervised learning, gaze-guided modeling, ML pipelines, SQL, BigQuery, and Apache Airflow.

\end{rSection}

\begin{rSection}{Skills}
\textbf{Programming:} Python, SQL, Bash \\
\textbf{Machine Learning:} PyTorch, Deep Learning, Computer Vision, Image Segmentation, Object Detection, Explainable AI, Weakly Supervised Learning \\
\textbf{Multimodal AI:} Vision-Language Models, Visual Grounding, Medical Image Analysis, Gaze Modeling, Agentic AI \\
\textbf{Data and Infrastructure:} BigQuery, Apache Airflow, Google Apps Script, Git, Linux
\end{rSection}

\begin{rSection}{Education}

{\bf PhD in Computer Engineering} \hfill {\bf Aug 2024 – Present} \\
University of Houston, USA \\
Topic: AI in Medicine; Focus: Computational Pathology, Trustworthy AI, Gaze-Guided Explainability

{\bf MSc in Mathematical Foundations of Computer Science (Data Science)}  \\ %2021 - 2023
Vietnam National University – Ho Chi Minh City, Vietnam \quad GPA 8.97/10

% Thesis: Conditional Distribution-based Imputation of Missing Values
{\bf Bachelor of Business Administration} \\
University of Economics and Law, Ho Chi Minh City, Vietnam
%2013 - 2016
\end{rSection}
%-----------------
\begin{rSection}{Experience}

\textbf{Research Assistant} \hfill \textbf{Aug 2024 – Present} \\
Department of Computer Engineering, University of Houston, USA \\
Supervisor: Prof. Hien Van Nguyen

\begin{itemize}
    \item Develop explainable AI and computer vision methods for whole-slide pathology image analysis using deep learning, weakly supervised learning, visual grounding, and model attribution.
    \item Build multimodal AI models that integrate medical images, clinical text, and eye-gaze data to align model reasoning with expert diagnostic behavior.
    \item Implement research pipelines in Python and PyTorch for image segmentation, feature attribution, prototype learning, and multimodal representation learning.
    \item Published first-author papers at WACV 2026, ISBI 2026, and MIDL 2026; contributed to MICCAI 2025, Scientific Reports, and Knowledge-Based Systems.
\end{itemize}

\textbf{Research Assistant} - Research Internship (NSTC Scholarship Program, Taiwan)
  \hfill \textbf{Oct 2023 -- Jan 2024} \\
National Cheng Kung University - BME Lab (Cancer Organoid Research) \\
Supervisor: Prof. Ting-Yuan Tu
\begin{itemize}
    \item Applied deep learning and computer vision methods in a biomedical engineering lab to analyze functional behavior in human cardiac organoids, enabling real-time quantification of contraction dynamics from microscopy videos.
\end{itemize}

\textbf{Senior Data Analyst, Machine Learning Focus} \hfill \textbf{Jan 2019 -- Oct 2022} \\
Tiki Corporation, Vietnam
\begin{itemize}
  \item Designed and deployed production recommendation systems using collaborative filtering, content-based models, and hybrid machine learning approaches.
  \item Built scalable end-to-end data and ML pipelines using Python, SQL, BigQuery, and Apache Airflow.
  \item Evaluated machine learning models and product changes through A/B testing, performance monitoring, and business metric analysis.
  \item Led data-driven modeling projects involving customer segmentation, clustering, predictive analytics, and automated reporting.
\end{itemize}

\textbf{Data Analyst} \hfill \textbf{Nov 2017 -- Jan 2019} \\
GHN Logistics, Vietnam
\begin{itemize}
  \item Developed data warehouses, automated reporting systems, and analytical dashboards using Python, SQL, and Google Apps Script.
\end{itemize}
\end{rSection}
%-------------------------------------------
\begin{rSection}{Publications}
{\small $^{*}$Equal contribution}
\vspace{-0.5em}
\begin{itemize}
    \itemsep-0.35em
    \item
        \href{https://arxiv.org/pdf/2511.08464}{
            \ptitle{Contrastive Integrated Gradients: A Feature Attribution-Based Method for Explaining Whole Slide Image Classification.}
            }\\
          \underline{Anh Mai Vu}, T.L. Vo, N.L.Q. Bui, N.N.L. Binh, A. Awasthi, H.Q. Vo, T.H. Nguyen, Z. Han, C. Mohan, H.V. Nguyen \\
          \ptitleb{IEEE/CVF Winter Conference on Applications of Computer Vision (WACV)}, 2026
    \item \href{https://arxiv.org/pdf/2512.05922}{\ptitle{LPD: Learnable Prototypes with Diversity Regularization for Weakly Supervised Histopathology Segmentation.}} \\
      \underline{Anh Mai Vu*}, Khang Le*, T.K.T. Vo, H. Thach, N.L.Q. Bui, T.H. Nguyen, M.H.N. Le, Z. Han, C. Mohan, H.V. Nguyen \\
    \ptitleb{IEEE International Symposium on Biomedical Imaging (ISBI)}, 2026
    \item \href{https://arxiv.org/pdf/2512.10316}{\ptitle{ConStruct: Structural Distillation of Foundation Models for Prototype-Based Weakly Supervised Histopathology Segmentation.}} \\
      \underline{Anh M. Vu*}, Khang Le*, Ha Thach*, Trang T.K. Vo, Han H. Huynh, David Yang, Minh H.N. Le, Thanh-Huy Nguyen, Akash Awasthi, Chandra Mohan, Zhu Han, Hien Van Nguyen \\
      \ptitleb{Medical Imaging with Deep Learning (MIDL)}, 2026
    \item \href{https://www.sciencedirect.com/science/article/abs/pii/S0950705125014728}{\ptitle{Structural Chain of Thoughts for Radiology Education.}} \\
          A. Awasthi, B. Chung, \underline{A.M. Vu}, S. Khan, N. Le, Z. Deng, R. Agrawal, C.C. Wu, H. Van Nguyen \\
          \ptitleb{Knowledge-Based Systems (Elsevier)}, 2025 \textbf{(IF: 7.6, Q1)}
   \item \href{https://www.nature.com/articles/s41598-025-97935-y}{\ptitle{Modeling radiologists' cognitive processes using a digital gaze twin to enhance radiology training.}} \\
          A. Awasthi, \underline{Anh Mai Vu}, N. Le, Z. Deng, S. Maulik, R. Agrawal, C.C. Wu, H.V. Nguyen \\
          \ptitleb{Scientific Reports (Springer Nature)}, 2025 \textbf{(IF:3.9, Q1)}
    \item \href{https://link.springer.com/chapter/10.1007/978-3-032-04971-1_34}{\ptitle{MAARTA: Multi-Agentic Adaptive Radiology Teaching Assistant.}} \\
          A. Awasthi, B.V. Chung, \underline{Anh M. Vu}, N. Le, R. Agrawal, Z. Deng, C. Wu, H.V. Nguyen \\
          \ptitleb{International Conference on Medical Image Computing and Computer-Assisted Intervention (MICCAI)}, 2025
    \item \href{https://arxiv.org/pdf/2601.14563}{\ptitle{Scribble-Supervised Medical Image Segmentation with Dynamic Teacher Switching and Hierarchical Consistency.}} \\
    H.T. Nguyen, L.H. Cao, D.T. Chung, \underline{Anh Mai Vu}, T.-M. Nguyen, M.H.N. Le, P.K. Huynh, U. Bagci \\
    \ptitleb{IEEE International Symposium on Biomedical Imaging (ISBI)}, 2026
    \item \ptitle{IMACT-CXR: An Interactive Multi-Agent Conversational Tutoring System for Chest X-Ray Interpretation} \\
      Tuan-Anh Le, \underline{Anh Mai Vu}, David Yang, Akash Awasthi, Hien Van Nguyen \\
      \ptitleb{IEEE International Symposium on Biomedical Imaging (ISBI)}, 2026
    \item \ptitle{QwenVLConnector: A Fast, Unified Medical VLM Chatbot for Fine-Grained Clinical Perception and Text Generation.} \\
          T. Nguyen, T.H. Nguyen, G.M. Hoang, \underline{A.M. Vu}, U. Bagci \\
          \ptitleb{MICCAI 2025 FLARE Challenge}
    \item \href{https://link.springer.com/chapter/10.1007/978-3-032-05825-6_6}{\ptitle{Lightweight Dual-Task Framework for Semi-supervised Lesion Segmentation with Knowledge Distillation from SAM.}} \\
          X.-L. Huynh, H.-T. Pham, \underline{Anh Mai Vu}, T.-M. Nguyen, T.Q.K. Bui, T.-B. Nguyen, Q. Nguyen, M.H.N. Le, P.K. Huynh \\
          \ptitleb{MICCAI Workshop on Deep Generative Models (DGM)}, 2025
    \item \href{https://openaccess.thecvf.com/content/CVPR2024W/DEF-AI-MIA/papers/Nguyen_Blurry-Consistency_Segmentation_Framework_with_Selective_Stacking_on_Differential_Interference_Contrast_CVPRW_2024_paper.pdf}{\ptitle{Blurry-Consistency Segmentation Framework with Selective Stacking on Differential Interference Contrast 3D Breast Cancer Spheroid.}} \\
          T.H. Nguyen, T.K.N. Ngo, \underline{M.A. Vu}, T.Y. Tu \\
          \ptitleb{IEEE/CVF Conference on Computer Vision and Pattern Recognition (CVPR) Workshops}, 2024
    \item \href{https://link.springer.com/chapter/10.1007/978-3-031-53302-0_8}{\ptitle{Correlation visualization under missing values: a comparison between imputation and direct parameter estimation methods.}} \\
          \underline{M.A. Vu}$^{*}$, N.H. Pham$^{*}$, K.L. Vo$^{*}$, T. Nguyen, M.A. Riegler, P. Halvorsen, B.T. Nguyen \\
          \ptitleb{International Conference on Multimedia Modeling (MMM)}, 2024
    \item \ptitle{DualProtoSeg: Simple and Efficient Design with Text- and Image-Guided Prototype Learning for Weakly Supervised Histopathology Image Segmentation.} \\
      \underline{Anh Mai Vu*}, Khang P. Le*, Trang T.K. Vo*, Ha Thach, Huy Hung Nguyen, David Yang, Han H. Huynh, Quynh Nguyen, Tuan M. Pham, Tuan-Anh Le, Minh H.N. Le, Thanh-Huy Nguyen, Akash Awasthi, Chandra Mohan, Zhu Han, Hien Van Nguyen \\
      \ptitleb{Under Review}, 2026

\end{itemize}

\end{rSection}

\begin{rSection}{Service}
\textbf{Technical Chair}, Emerging LLM/LMM Applications in Medical Imaging (ELAMI) Workshop, MICCAI 2026 \hfill \textbf{2026} \\
University of Houston
\end{rSection}

\begin{rSection}{Awards}
\begin{itemize}
    \item MICCAI FLARE Challenge 2025 Finalist with Honorable Award. \href{https://drive.google.com/file/d/1MMi4t1MICseOa5s3F3MLBiRWls1amj__/view?usp=sharing}{[Cert]}
    \item AI Challenge 2023, National Video Retrieval Competition, Finalist.
\end{itemize}
\end{rSection}

\end{document}
